Daily goals

### 2020-07-02 1-abstract.Rmd
kinsey comments

1. Physcraper can be used by the nonspecialist, as a tool to generate phylogenetic
hypothesis based on already available expert phylogenetic knowledge.
Phylogeneticists and group specialists will find it useful as a tool to facilitate dataset gathering and comparison
of alternative phylogenetic hypotheses (topologies).

1. We hope that the Physcraper workflow demonstrates the benefits of opening results in phylogenetics, encouraging more researchers to strive for better data sharing practices. Physcraper can be used with any OS. Detailed instructions for installation and
use are available at [https://physcraper.readthedocs](https://physcraper.readthedocs.io/en/tutorial/index.html).

>>>>

1. Physcraper can be used by the nonspecialist, as a tool to generate phylogenetic
hypotheses based on already available expert phylogenetic knowledge.
Phylogeneticists and group specialists will find it useful as a tool to facilitate molecular dataset gathering and comparison
of alternative phylogenetic hypotheses (topologies).

1. We hope that the Physcraper workflow demonstrates the benefits of open science for phylogenetics, encouraging more researchers to strive for better sharing practices. Physcraper can be used with any OS. Detailed instructions for installation and
use are available at [https://physcraper.readthedocs](https://physcraper.readthedocs.io/en/tutorial/index.html).

### 2020-07-02 _TODO.Rmd
finished ejm comments
kinsey comments

@@

- [ ] on methods, bootstrap summary part cite:
 SumTrees: Phylogenetic Tree Summarization Version 4.4.0, from DendroPy 4.4.0 (main-bc20409)

- [ ] intro: challenge in connecting different parts of the database with other databases that might refer to the same thing. For example taxon ids represent own challenge in this sense, but it has been solved by the otol taxonomy project. Othe rchallenge is the study ids. This is not fully resolved yet by otol, but only partially by linking to the alignment repo.
- [ ] intro: programatic access.

>>>>

- [ ] add interactive table of csv metadata to physcraper examples

@@

- [x] on methods, bootstrap summary part cite:
 SumTrees: Phylogenetic Tree Summarization Version 4.4.0, from DendroPy 4.4.0 (main-bc20409)

- [ ] intro: challenge in connecting different parts of the database with other databases that might refer to the same thing. For example taxon ids represent own challenge in this sense, but it has been solved by the otol taxonomy project. Othe rchallenge is the study ids. This is not fully resolved yet by otol, but only partially by linking to the alignment repo.

- [ ] intro: programatic access.
